### 2016-06-16 paper/paper.tex
paper basics

\documentclass[letterpaper, 12pt]{article}
\usepackage{circuitikz}
\usepackage[pdf]{pstricks}
\usepackage{pst-optic}

\title{Modern Physics Laser Scanning Project}
\author{Alvin Lin
  \thanks{with Jion Fairchild and Sachal Malick}}
\date{June 2016}

\begin{document}

\begin{titlepage}
\maketitle
\end{titlepage}

\begin{abstract}
This experiment was conducted in the Modern Physics class of 2016 at Stuyvesant High School. The goal was to build a laser scanner using a laser and a photodiode and find the maximum achievable resolution the apparatus.
\end{abstract}

\section{Experimental Setup}
In this experiment, we focused a laser onto a piece of paper containing our
scanning sample and read the amount of reflected light using a photometer. Conveniently, the photometer outputted the a voltage linearly proportional to the amount of light it received in addition to its digital display. This allowed us to connect an Arduino microcontroller to the photometer to read and store the voltages as we passed the scanning sample beneath the laser. We 3D printed two important parts to our scanner, the slides for the x and y axes.
\par
In order to maximize the resolution of our image, we wanted the laser beam to be as small and as focused as possible. Before having it

\begin{pspicture}[showgrid](0,-0.3)(3,2.3)
\end{pspicture}

\begin{pspicture}[showgrid](0,-0.3)(3,2.3)
\pnodes(0,1){A}(3,1){B}
\lens(A)(B)
\end{pspicture}

\end{document}

### 2016-06-17 paper/paper.tex
stuff

@@
 \usepackage{circuitikz}
+\usepackage{listings}
 \usepackage[pdf]{pstricks}
-\usepackage{pst-optic}
+\usepackage{pst-optexp}
+
+\setlength{\parskip}{1em}
 
@@
 This experiment was conducted in the Modern Physics class of 2016 at Stuyvesant High School.
-The goal was to build a laser scanner using a laser and a photodiode and find the maximum achievable resolution the apparatus.
+The goal was to build a laser scanner using a laser and a photodiode and find the maximum achievable resolution of the apparatus.
 \end{abstract}
@@
 \section{Experimental Setup}
+\par
 In this experiment, we focused a laser onto a piece of paper containing our
 scanning sample and read the amount of reflected light using a photometer.
-Conveniently, the photometer outputted the a voltage linearly proportional to the amount of light it received in addition to its digital display.
+The photometer displayed the amount of light it received on a digital display but also conveniently had two banana jacks that outputted a voltage linearly proportional to the amount of light it received.
 This allowed us to connect an Arduino microcontroller to the photometer to read and store the voltages as we passed the scanning sample beneath the laser.
@@
 \par
-In order to maximize the resolution of our image, we wanted the laser beam to be as small and as focused as possible. Before having it
+In order to maximize the resolution of our image, we wanted the laser beam to be as small and as focused as possible.
+We spaced three concave lenses in front of the laser to expand the beam, collimate it, and focus it to a point.
+The scanning sample would be placed at the end of the focused beam.
+If the laser was focused on a darker point on the sample, it would reflect less light.
+Conversely, if the laser was focused on a lighter point, it would reflect more light.
 
-\begin{pspicture}[showgrid](0,-0.3)(3,2.3)
+\begin{pspicture}[](0,0)(14,4)
+  \pnodes(2,2){A}(12,2){B}
+  \pnodes(10.5,1.5){D}(10.7,2){E}(10.9,2.5){F}
+  \begin{optexp}
+    \optbox[position=start](A)(B){laser}
+    \lens[lensradius=0.75,abspos=1,labeloffset=-1](A)(B){expands beam}
+    \lens[lensradius=2.3,abspos=4](A)(B){collimates beam}
+    \lens[lensradius=0.75,abspos=8](A)(B){focuses beam}
+    \mirror[labeloffset=-0.7](D)(E)(F){sample}
+    \drawwidebeam[beamwidth=0.2,linecolor=red]{-}(B)
+  \end{optexp}
 \end{pspicture}
 
-\begin{pspicture}[showgrid](0,-0.3)(3,2.3)
-\pnodes(0,1){A}(3,1){B}
-\lens(A)(B)
-\end{pspicture}
+\par
+We built our own 2D slide mechanism to shift the scanning sample back and forth under the laser.
+We used an Arduino to read the voltage output from the photometer and simultaneously control two stepper motors which would shift the sample back and forth.
+
+\begin{circuitikz}
+  \draw
+  (0,0) to [battery](3,0)
+  to [european resistor](6,0)
+  to [american resistor](7,3)
+  to [short](4,1)
+  to [short](4,0);
+\end{circuitikz}
+
+\begin{lstlisting}[language=C,showstringspaces=false]
+  /**
+   * Base code for Arduino when scanning 1 dimensionally.
+   */
+
+  #include <Stepper.h>
+
+  // Globals
+  #define BAUDRATE 9600
+  #define NUM_POLLS 10
+
+  #define SCAN_SPEED 60
+  #define SCAN_STEPS 700
+  #define SCAN_INTERVAL 1
+
+  Stepper motor(512, 8, 10, 9, 11);
+
+  void setup() {
+    Serial.begin(BAUDRATE);
+    for (int i = 8; i < 12; ++i) {
+      pinMode(i, OUTPUT);
+    }
+    motor.setSpeed(SCAN_SPEED);
+  }
+
+  void loop() {
+    String data = Serial.readString();
+    float value_sum = 0;
+    Serial.println(data);
+    if (data == "begin") {
+      Serial.println("{ \"type\": \"1d\" }");
+      for (int i = 0; i < SCAN_STEPS; ++i) {
+        value_sum = 0;
+        for (int j = 0; j < NUM_POLLS; ++j) {
+          value_sum += analogRead(A0);
+        }
+        Serial.println(value_sum / 10.0);
+        motor.step(SCAN_INTERVAL);
+      }
+      Serial.println("end");
+      motor.step(-SCAN_INTERVAL * SCAN_STEPS);
+    }
+  }
+\end{lstlisting}
 

### 2016-06-17 paper/paper.tex
update to paper

@@
 \documentclass[letterpaper, 12pt]{article}
-\usepackage{circuitikz}
+\usepackage{graphicx}
+\graphicspath{ {pictures/} }
 \usepackage{listings}
@@
 
-\begin{circuitikz}
-  \draw
-  (0,0) to [battery](3,0)
-  to [european resistor](6,0)
-  to [american resistor](7,3)
-  to [short](4,1)
-  to [short](4,0);
-\end{circuitikz}
+\begin{figure}
+  \centering
+  \includegraphics[width=12cm,height=9cm]{circuit}
+  \caption{Diagram of Components}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=9cm,height=12cm]{setup}
+  \caption[caption]{3D printed components, CADs available here:\hspace{\textwidth}https://www.github.com/omgimanerd/im-firing-my-lazer}
+\end{figure}
+
+\section{Experimental Procedure}
 
 \begin{lstlisting}[language=C,showstringspaces=false]
-  /**
-   * Base code for Arduino when scanning 1 dimensionally.
-   */
 

### 2016-06-17 paper/paper.tex
update paper

@@
 \section{Experimental Procedure}
+\par
+We set up various resolution test targets beneath our scanner and ran our scanner over each target.
+Based on the stepper motors and driver boards we were using\footnotemark, we approximated what the resolution of our setup would be.
+\footnotetext{We were using the USPRO 5V 4-phase 5-wire stepper motors with the ULN2003 driver board for Arduino}
+Due to the driver board's microstepping, each revolution of the motor took 2048 steps.
+With a 0.5 inch diameter drive axle moving the sample, this means that 1 step equated to \( 7.6699 \times 10^{-4} \) inches.
+Converting this to \( \frac{lines}{mm}\):
 
-\begin{lstlisting}[language=C,showstringspaces=false]
+\[ 7.6699\times10^{-4}in = 1.9557746\times10^{-2}mm \]
+\[ \frac{1\ line}{1.9557746\times10^{-2}mm} = 51.13\frac{lines}{mm}\]
+\[ 51.13\frac{lines}{mm} \div 2 \approx 25\frac{lines}{mm} \]
 
-  #include <Stepper.h>
-
-  // Globals
-  #define BAUDRATE 9600
-  #define NUM_POLLS 10
-
-  #define SCAN_SPEED 60
-  #define SCAN_STEPS 700
-  #define SCAN_INTERVAL 1
-
-  Stepper motor(512, 8, 10, 9, 11);
-
-  void setup() {
-    Serial.begin(BAUDRATE);
-    for (int i = 8; i < 12; ++i) {
-      pinMode(i, OUTPUT);
-    }
-    motor.setSpeed(SCAN_SPEED);
-  }
-
-  void loop() {
-    String data = Serial.readString();
-    float value_sum = 0;
-    Serial.println(data);
-    if (data == "begin") {
-      Serial.println("{ \"type\": \"1d\" }");
-      for (int i = 0; i < SCAN_STEPS; ++i) {
-        value_sum = 0;
-        for (int j = 0; j < NUM_POLLS; ++j) {
-          value_sum += analogRead(A0);
-        }
-        Serial.println(value_sum / 10.0);
-        motor.step(SCAN_INTERVAL);
-      }
-      Serial.println("end");
-      motor.step(-SCAN_INTERVAL * SCAN_STEPS);
-    }
-  }
-\end{lstlisting}
+\par
+This number is only true, however, if our laser beam is an infinitesimally small point. Since this is not the case, our actual resolution is much lower.
 

### 2016-06-17 paper/paper.tex
cleanup + diagrams
thingies and updates

@@
 \documentclass[letterpaper, 12pt]{article}
+\usepackage{float}
 \usepackage{graphicx}
@@
 \usepackage{listings}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.9}
 \usepackage[pdf]{pstricks}
 \usepackage{pst-optexp}
+\usepackage{hyperref}
+\hypersetup{colorlinks=true,linkcolor=blue,filecolor=magenta,urlcolor=cyan}
 
@@
 scanning sample and read the amount of reflected light using a photometer.
-The photometer displayed the amount of light it received on a digital display but also conveniently had two banana jacks that outputted a voltage linearly proportional to the amount of light it received.
+The photometer displayed the amount of light it received on a digital display but also conveniently had two banana jacks that outputted a voltage proportional to the amount of light it received.
 This allowed us to connect an Arduino microcontroller to the photometer to read and store the voltages as we passed the scanning sample beneath the laser.
@@
 The scanning sample would be placed at the end of the focused beam.
-If the laser was focused on a darker point on the sample, it would reflect less light.
-Conversely, if the laser was focused on a lighter point, it would reflect more light.
+If the laser was focused on a darker point on the sample, it would reflect less light and the photometer would read a lower voltage.
+Conversely, if the laser was focused on a lighter point, it would reflect more light and the photometer would read a higher voltage.
 
@@
 
-\begin{figure}
+\begin{figure}[H]
   \centering
-  \includegraphics[width=12cm,height=9cm]{circuit}
+  \includegraphics[width=10cm,height=6cm]{circuit}
   \caption{Diagram of Components}
@@
 
-\begin{figure}
+\begin{figure}[H]
   \centering
-  \includegraphics[width=9cm,height=12cm]{setup}
-  \caption[caption]{3D printed components, CADs available here:\hspace{\textwidth}https://www.github.com/omgimanerd/im-firing-my-lazer}
+  \includegraphics[width=6cm,height=10cm]{setup}
+  \caption[caption]{3D printed components\footnotemark}
 \end{figure}
+\footnotetext{CADs of these components are available here:
+  \url{https://www.github.com/omgimanerd/im-firing-my-lazer}}
 
@@
 \par
-We set up various resolution test targets beneath our scanner and ran our scanner over each target.
-Based on the stepper motors and driver boards we were using\footnotemark, we approximated what the resolution of our setup would be.
-\footnotetext{We were using the USPRO 5V 4-phase 5-wire stepper motors with the ULN2003 driver board for Arduino}
+We set up various resolution test targets beneath our scanner and ran our scanner over each target. Based on the stepper motors\footnotemark
+\footnotetext{USPRO 5V 4-phase 5-wire stepper motors}
+and driver boards\footnotemark
+\footnotetext{ULN2003 driver board for Arduino}
+we were using, we approximated what the resolution of our setup would be.
 Due to the driver board's microstepping, each revolution of the motor took 2048 steps.
-With a 0.5 inch diameter drive axle moving the sample, this means that 1 step equated to \( 7.6699 \times 10^{-4} \) inches.
-Converting this to \( \frac{lines}{mm}\):
+With a 0.5 inch diameter drive axle moving the sample, this means that 1 step equated to $7.6699\times10^{-4}$ inches.
+Converting this to $ \frac{lines}{mm}$:
 
-\[ 7.6699\times10^{-4}in = 1.9557746\times10^{-2}mm \]
-\[ \frac{1\ line}{1.9557746\times10^{-2}mm} = 51.13\frac{lines}{mm}\]
-\[ 51.13\frac{lines}{mm} \div 2 \approx 25\frac{lines}{mm} \]
+$$ 7.6699\times10^{-4}in = 1.9557746\times10^{-2}mm $$
+$$ \frac{1\ line}{1.9557746\times10^{-2}mm} = 51.13\frac{lines}{mm} $$
+$$ 51.13\frac{lines}{mm} \div 2 \approx 25\frac{lines}{mm} $$
 
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=8cm,height=6cm]{resolution_test}
+  \caption[caption]{Example Resolution Test Targets (not to scale)}
+\end{figure}
+
+\section{Experimental Results}
+\par
+Running the laser scanner over the actual resolution test targets above gave us a much clearer indicator of whether or not our scanner was actually able to resolve up to 25 $\frac{lines}{mm}$.
+We ran the laser directly over the four lines in each resolution test target while reading in the values, starting with the lowest resolution.
+
+\pgfplotstableread{scan_1.6.txt}
+  \dataone
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}
+    \begin{axis}[
+      xlabel={$time$},
+      ylabel={$relative\ intensity$},
+      xticklabels={,,},
+      yticklabels={,,}]
+      \addplot[mark=none] table from \dataone;
+    \end{axis}
+  \end{tikzpicture}
+  \caption[caption]{Scan of 1.6 {$\frac{lines}{mm}$} resolution test target}
+\end{figure}
+
+\par
+In figure 4, four discrete dips in the relative intensity read by the Arduino are visible as the laser passes over the 1.6 $\frac{lines}{mm}$ resolution test target.
+Each dip is distinguishable and corresponds to a line on the resolution test target.
+As long as each dip in the relative intensity is discrete for that test, we will consider it a resolvable resolution.
+
+\pgfplotstableread{scan_1.8.txt}
+  \datatwo
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}
+    \begin{axis}[
+      xlabel={$time$},
+      ylabel={$relative\ intensity$},
+      xticklabels={,,},
+      yticklabels={,,}]
+      \addplot[mark=none] table from \datatwo;
+    \end{axis}
+  \end{tikzpicture}
+  \caption[caption]{Scan of 1.8 {$\frac{lines}{mm}$} resolution test target}
+\end{figure}
+
+\pgfplotstableread{scan_2.0.txt}
+  \datathree
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}
+    \begin{axis}[
+      xlabel={$time$},
+      ylabel={$relative\ intensity$},
+      xticklabels={,,},
+      yticklabels={,,}]
+      \addplot[mark=none] table from \datathree;
+    \end{axis}
+  \end{tikzpicture}
+  \caption[caption]{Scan of 2.0 {$\frac{lines}{mm}$} resolution test target}
+\end{figure}
+
+\pgfplotstableread{scan_2.2.txt}
+  \datathree
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}
+    \begin{axis}[
+      xlabel={$time$},
+      ylabel={$relative\ intensity$},
+      xticklabels={,,},
+      yticklabels={,,}]
+      \addplot[mark=none] table from \datathree;
+    \end{axis}
+  \end{tikzpicture}
+  \caption[caption]{Scan of 2.2 {$\frac{lines}{mm}$} resolution test target}
+\end{figure}
+
+\pgfplotstableread{scan_2.5.txt}
+  \datathree
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}
+    \begin{axis}[
+      xlabel={$time$},
+      ylabel={$relative\ intensity$},
+      xticklabels={,,},
+      yticklabels={,,}]
+      \addplot[mark=none] table from \datathree;
+    \end{axis}
+  \end{tikzpicture}
+  \caption[caption]{Scan of 2.5 {$\frac{lines}{mm}$} resolution test target}
+\end{figure}
+
+\pgfplotstableread{scan_2.8.txt}
+  \datathree
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}
+    \begin{axis}[
+      xlabel={$time$},
+      ylabel={$relative\ intensity$},
+      xticklabels={,,},
+      yticklabels={,,}]
+      \addplot[mark=none] table from \datathree;
+    \end{axis}
+  \end{tikzpicture}
+  \caption[caption]{Scan of 2.8 {$\frac{lines}{mm}$} resolution test target}
+\end{figure}
+
+\pgfplotstableread{scan_3.2.txt}
+  \datathree
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}
+    \begin{axis}[
+      xlabel={$time$},
+      ylabel={$relative\ intensity$},
+      xticklabels={,,},
+      yticklabels={,,}]
+      \addplot[mark=none] table from \datathree;
+    \end{axis}
+  \end{tikzpicture}
+  \caption[caption]{Scan of 3.2 {$\frac{lines}{mm}$} resolution test target}
+\end{figure}
+
+\pgfplotstableread{scan_4.0.txt}
+  \datathree
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}
+    \begin{axis}[
+      xlabel={$time$},
+      ylabel={$relative\ intensity$},
+      xticklabels={,,},
+      yticklabels={,,}]
+      \addplot[mark=none] table from \datathree;
+    \end{axis}
+  \end{tikzpicture}
+  \caption[caption]{Scan of 4.0 {$\frac{lines}{mm}$} resolution test target}
+\end{figure}
+
+\section{Analysis}
+\par
+Figures 5 to 11 show our scan data as we increase the resolution of our test target.
+As we increase the resolution of the test target, the variance in relative intensity between the lines and the space between them becomes muddled.
+It is possible to see five discrete dips only up to 3.2 $\frac{lines}{mm}$.
+At 4.0 $\frac{lines}{mm}$, it is no longer possible to discern five discrete dips in the relative intensity detected.
+Our testable scanner resolution limit, therefore, is 3.2 $\frac{lines}{mm}$.
+\par
+Likely, we could improve our resolution by focusing the laser to a smaller point.
+Due to human error, our lenses were likely not optimally aligned and we did not focus the laser to a small enough point.
+Additionally, we could improve the scanner by reducing the radius of the axle pulling the sample across the laser, which would reduce the step distance per step.
+
 \end{document}

### 2016-06-17 data/convert.py

@@ -1,0 +1,16 @@
+#!/usr/bin/python
+
+import json
+import sys
+
+if __name__ == "__main__":
+
+    if len(sys.argv) < 2:
+        print "No file specified"
+
+    with open(sys.argv[1]) as f:
+        data = json.loads(f.read()).get("values")
+    with open("%s.txt"% sys.argv[1][:-5], "w") as f:
+        f.write("x y\n")
+        for i in range(len(data)):
+            f.write("%d %s\n" % (i, data[i]))

### 2016-06-18 paper/paper.tex
finished paper, updated README

@@
 \documentclass[letterpaper, 12pt]{article}
+\renewcommand{\refname}{References and Resources}
+\usepackage[utf8]{inputenc}
 \usepackage{float}
 \usepackage{graphicx}
-\graphicspath{ {pictures/} }
+\graphicspath{{pictures/}}
 \usepackage{listings}
@@
 This allowed us to connect an Arduino microcontroller to the photometer to read and store the voltages as we passed the scanning sample beneath the laser.
-We 3D printed two important parts to our scanner, the slides for the x and y axes.
+To shift the sample vertically and horizontally during scanning, we 3D printed slides for the sample which we motorized using stepper motors.
 \par
@@
 We spaced three concave lenses in front of the laser to expand the beam, collimate it, and focus it to a point.
-The scanning sample would be placed at the end of the focused beam.
+The scanning sample would be placed at the focal point of the last concave lense.
 If the laser was focused on a darker point on the sample, it would reflect less light and the photometer would read a lower voltage.
@@
 \par
-We built our own 2D slide mechanism to shift the scanning sample back and forth under the laser.
-We used an Arduino to read the voltage output from the photometer and simultaneously control two stepper motors which would shift the sample back and forth.
+The Arduino that we used to read in the voltage values from the photometer was also used to simultaneously control the stepper motors moving the sample.
+For one dimensional scans, we only moved one motor and scanned a single line across the target.
+For two dimensional scans, we oscillated the motor in one direction while shifting it slowly perpendicular to its direction of oscillation.
 
@@
   \centering
-  \includegraphics[width=10cm,height=6cm]{circuit}
+  \includegraphics[width=10cm,height=6cm]{setup_diagram}
   \caption{Diagram of Components}
@@
   \centering
-  \includegraphics[width=6cm,height=10cm]{setup}
+  \includegraphics[width=6cm,height=7cm]{setup_picture}
   \caption[caption]{3D printed components\footnotemark}
 \end{figure}
-\footnotetext{CADs of these components are available here:
+\footnotetext{CADs available here\cite{github}:
   \url{https://www.github.com/omgimanerd/im-firing-my-lazer}}
@@
 We set up various resolution test targets beneath our scanner and ran our scanner over each target. Based on the stepper motors\footnotemark
-\footnotetext{USPRO 5V 4-phase 5-wire stepper motors}
+\footnotetext{USPRO 28BYJ 5V 4-phase 5-wire stepper motors\cite{amazon}}
 and driver boards\footnotemark
-\footnotetext{ULN2003 driver board for Arduino}
+\footnotetext{ULN2003 driver board for Arduino\cite{amazon}}
 we were using, we approximated what the resolution of our setup would be.
-Due to the driver board's microstepping, each revolution of the motor took 2048 steps.
-With a 0.5 inch diameter drive axle moving the sample, this means that 1 step equated to $7.6699\times10^{-4}$ inches.
-Converting this to $ \frac{lines}{mm}$:
+Due to the driver board's microstepping, each revolution of the motor took 512 steps.
+With a 0.5 inch diameter drive axle moving the sample, this means that 1 step of the motor would shift the sample $3.067962\times10^{-3}$ inches.
+Converting this to $\frac{lines}{mm}$:
 
-$$ 7.6699\times10^{-4}in = 1.9557746\times10^{-2}mm $$
+$$ 3.067962\times10^{-3}in = 1.9557746\times10^{-2}mm $$
 $$ \frac{1\ line}{1.9557746\times10^{-2}mm} = 51.13\frac{lines}{mm} $$
@@
   \includegraphics[width=8cm,height=6cm]{resolution_test}
-  \caption[caption]{Example Resolution Test Targets (not to scale)}
+  \caption[caption]{Example Resolution Test Targets (not to scale)\cite{test_chart}}
 \end{figure}
 
-\section{Experimental Results}
+\section{Experimental Results for 1 Dimensional Scans}
 \par
@@
   \end{tikzpicture}
-  \caption[caption]{Scan of 1.6 {$\frac{lines}{mm}$} resolution test target}
+  \caption[caption]{Scan of 1.6 $\frac{lines}{mm}$ resolution test target}
 \end{figure}
@@
   \end{tikzpicture}
-  \caption[caption]{Scan of 1.8 {$\frac{lines}{mm}$} resolution test target}
+  \caption[caption]{Scan of 1.8 $\frac{lines}{mm}$ resolution test target}
 \end{figure}
@@
   \end{tikzpicture}
-  \caption[caption]{Scan of 2.0 {$\frac{lines}{mm}$} resolution test target}
+  \caption[caption]{Scan of 2.0 $\frac{lines}{mm}$ resolution test target}
 \end{figure}
@@
   \end{tikzpicture}
-  \caption[caption]{Scan of 2.2 {$\frac{lines}{mm}$} resolution test target}
+  \caption[caption]{Scan of 2.2 $\frac{lines}{mm}$ resolution test target}
 \end{figure}
@@
   \end{tikzpicture}
-  \caption[caption]{Scan of 2.5 {$\frac{lines}{mm}$} resolution test target}
+  \caption[caption]{Scan of 2.5 $\frac{lines}{mm}$ resolution test target}
 \end{figure}
@@
   \end{tikzpicture}
-  \caption[caption]{Scan of 2.8 {$\frac{lines}{mm}$} resolution test target}
+  \caption[caption]{Scan of 2.8 $\frac{lines}{mm}$ resolution test target}
 \end{figure}
@@
   \end{tikzpicture}
-  \caption[caption]{Scan of 3.2 {$\frac{lines}{mm}$} resolution test target}
+  \caption[caption]{Scan of 3.2 $\frac{lines}{mm}$ resolution test target}
 \end{figure}
@@
   \end{tikzpicture}
-  \caption[caption]{Scan of 4.0 {$\frac{lines}{mm}$} resolution test target}
+  \caption[caption]{Scan of 4.0 $\frac{lines}{mm}$ resolution test target}
 \end{figure}
@@
 \par
-Likely, we could improve our resolution by focusing the laser to a smaller point.
-Due to human error, our lenses were likely not optimally aligned and we did not focus the laser to a small enough point.
-Additionally, we could improve the scanner by reducing the radius of the axle pulling the sample across the laser, which would reduce the step distance per step.
+We could likely improve our resolution by focusing the laser to a smaller point.
+Due to human error, our lenses were probably not optimally aligned and we did not focus the laser to a small enough point.
+Additionally, we could improve the scanner by reducing the radius of the axle pulling the sample across the laser, which would reduce the step distance and increase the precision.
+
+\section{Experimental Results for 2 Dimensional Scans}
+\par
+For two dimensional scans, instead of running the sample in one direction under the laser, we oscillated it back and forth in the $y$ direction while slowing shifting it in the $x$ direction.
+This allowed us to produce a two-dimensional image of the lines on the resolution test target.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=8cm,height=6cm]{2d_scan_1}
+  \caption[caption]{Two Dimensional Scan of the 1.6 $\frac{lines}{mm}$ Test Target}
+\end{figure}
+
+\par
+For demonstration purposes, we used a lower resolution test target so that we could produce a discernible image.
+We scaled the voltage received by the Arduino to a greyscale value and plotted it based on the motor's position to create the image.
+However, the motor would slightly drift after each oscillation, creating the slant in the line visible in the scan above.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=8cm,height=6cm]{2d_scan_2}
+  \caption[caption]{Two Dimensional Scan with Drift Adjustment}
+\end{figure}
+
+\par
+We were able to reduce some of the slanting by manually accounting for the drift in the motors.
+Some noise is visible in both of the scans due to the flexing of test target since it was printed on standard printer paper.
+
+\newpage
+
+\begin{thebibliography}{9}
+
+  \bibitem{amazon}
+  Amazon.
+  \textit{USPRO 28BYJ Stepper Motors + ULN2003 Driver Board}
+  \texttt{https://www.amazon.com/USPRO-Stepper-28BYJ-48-4-Phase-ULN2003/}
+  \texttt{dp/B00JB22IQC}
+
+  \bibitem{arduino}
+  Arduino.
+  \textit{References and Guides}\newline
+  \texttt{https://www.arduino.cc/}
+
+  \bibitem{github}
+  GitHub.
+  \textit{im-firing-my-lazer repository}
+  Alvin Lin, 2016\newline
+  \texttt{https://www.github.com/omgimanerd/im-firing-my-lazer}
+
+  \bibitem{laser_scanning_paper}
+  Peter Axelsson.
+  \textit{Processing of laser scanner data - algorithms and applications}.
+  Department of Geodesy and Photogrammetry, Royal Institute of Technology, Stockholm, Sweden, 1998.\newline
+  \texttt{http://warnercnr.colostate.edu/~lefsky/isprs/1133.pdf}
+
+  \bibitem{thinkquest}
+  ThinkQuest.
+  \textit{Lenses and optics}
+  American Physical Society, 2006\newline
+  \texttt{http://www.physicscentral.com/experiment/physicsquest/past/upload/}
+  \texttt{pq06-Extension4.pdf}
+
+  \bibitem{test_chart}
+  USAF Test Chart
+  \textit{High Definition Test Slides}
+  Pyser-SGI\newline
+  \texttt{http://www.pyser-sgi.com/graticules/graticules-news/usaf-test-chart-}
+  \texttt{gets-higher-definition}
+
+\end{thebibliography}
+
+\newpage
+
+\appendix
+\section{Appendix A: Code Resources}
+
+\subsection{Arduino code for 1 dimensional scanning}
+\begin{lstlisting}[language=C]
+#include <Stepper.h>
+
+// Globals
+#define BAUDRATE 9600
+#define NUM_POLLS 10
+
+#define SCAN_SPEED 60
+#define SCAN_STEPS 700
+#define SCAN_INTERVAL 1
+
+Stepper motor(512, 8, 10, 9, 11);
+
+void setup() {
+  Serial.begin(BAUDRATE);
+  for (int i = 8; i < 12; ++i) {
+    pinMode(i, OUTPUT);
+  }
+  motor.setSpeed(SCAN_SPEED);
+}
+
+void loop() {
+  String data = Serial.readString();
+  float value_sum = 0;
+  Serial.println(data);
+  if (data == "begin") {
+    Serial.println("{ \"type\": \"1d\" }");
+    for (int i = 0; i < SCAN_STEPS; ++i) {
+      value_sum = 0;
+      for (int j = 0; j < NUM_POLLS; ++j) {
+        value_sum += analogRead(A0);
+      }
+      Serial.println(value_sum / 10.0);
+      motor.step(SCAN_INTERVAL);
+    }
+    Serial.println("end");
+    motor.step(-SCAN_INTERVAL * SCAN_STEPS);
+  }
+}
+\end{lstlisting}
+
+\subsection{Arduino code for 2 dimensional scanning}
+\begin{lstlisting}[language=C]
+#include <Stepper.h>
+
+// Globals
+#define BAUDRATE 9600
+#define NUM_POLLS 10
+
+#define SCAN_SPEED 40
+#define X_SCAN_STEPS 20
+#define X_SCAN_INTERVAL 50
+#define Y_SCAN_STEPS 150
+#define Y_SCAN_INTERVAL 5
+
+// The motor drifts some amount every y-iteration. This constant fights against that.
+#define DRIFT_CONSTANT -50
+
+Stepper x_motor(512, 4, 6, 5, 7);
+Stepper y_motor(512, 8, 10, 9, 11);
+
+void setup() {
+  Serial.begin(BAUDRATE);
+  for (int i = 4; i < 12; ++i) {
+    pinMode(i, OUTPUT);
+  }
+  x_motor.setSpeed(SCAN_SPEED);
+  y_motor.setSpeed(SCAN_SPEED);
+}
+
+void loop() {
+  String data = Serial.readString();
+  float value_sum = 0;
+  Serial.println(data);
+  if (data == "begin") {
+    Serial.print("{ \"type\": \"2d\", \"width\": ");
+    Serial.print(Y_SCAN_STEPS);
+    Serial.print(", \"height\": ");
+    Serial.print(X_SCAN_STEPS);
+    Serial.print(" }\n");
+    for (int x = 0; x < X_SCAN_STEPS; ++x) {
+      for (int y = 0; y < Y_SCAN_STEPS; ++y) {
+        value_sum = 0;
+        for (int i = 0; i < NUM_POLLS; ++i) {
+          value_sum += analogRead(A0);
+          delay(2);
+        }
+        Serial.println(value_sum / 10.0);
+        y_motor.step(Y_SCAN_INTERVAL);
+      }
+      y_motor.step(-(Y_SCAN_INTERVAL * Y_SCAN_STEPS - DRIFT_CONSTANT));
+      x_motor.step(X_SCAN_INTERVAL);
+    }
+    Serial.println("end");
+    x_motor.step(-X_SCAN_INTERVAL * X_SCAN_STEPS);
+    y_motor.step(-Y_SCAN_INTERVAL * Y_SCAN_STEPS);
+  }
+}
+\end{lstlisting}
+
+\subsection{Python code to visualize the stored data}
+\begin{lstlisting}[language=Python]
+#!/usr/bin/python
+
+from matplotlib import pyplot
+from PIL import Image
+
+import argparse
+import json
+import numpy as np
+
+class Visualizer:
+
+    @staticmethod
+    def visualize(data):
+        visualize_functions = {
+            "1d": Visualizer.visualize_1d,
+            "2d": Visualizer.visualize_2d
+        }
+        visualize_functions[data["type"]](data)
+
+    @staticmethod
+    def visualize_1d(data):
+        figure = pyplot.figure()
+        figure.suptitle("Intensity vs motor ticks")
+        values = data["values"]
+        pyplot.plot(range(len(values)), values)
+        pyplot.xlabel("Motor ticks")
+        pyplot.ylabel("Relative Intensity")
+        pyplot.grid()
+        pyplot.show()
+
+    @staticmethod
+    def _linear_scale(x, a1, a2, b1, b2):
+        return ((x - a1) * (b2 - b1) / (a2 - a1)) + b1
+
+    @staticmethod
+    def _to_pil_data(values):
+        low, high = min(values), max(values)
+        return map(lambda x: Visualizer._linear_scale(x, low, high, 0, 255),
+                   values)
+
+    @staticmethod
+    def visualize_2d(data):
+        width = data["width"]
+        height = data["height"]
+        image = Image.new("1", (width, height))
+        image.putdata(Visualizer._to_pil_data(data["values"]))
+        image = image.resize((width * 8, height * 8), Image.ANTIALIAS)
+        image.show()
+
+if __name__ == "__main__":
+    parser = argparse.ArgumentParser()
+    parser.add_argument("filename", help="The JSON file containing the data")
+    args = parser.parse_args()
+    with open(args.filename) as data_file:
+        Visualizer.visualize(json.loads(data_file.read().strip()))
+\end{lstlisting}
+
+\subsection{Python code to read the data from the serial port}
+\begin{lstlisting}
+#!/usr/bin/python
+
+from lib.visualizer import Visualizer
+
+import argparse
+import json
+import serial
+import sys
+import time
+
+class Scanner():
+
+    BAUDRATE = 9600
+    AMPLIFYING_FACTOR = 3
+
+    def __init__(self, serial):
+        self.serial = serial
+
+    @staticmethod
+    def create(location):
+        return Scanner(serial.Serial(location, Scanner.BAUDRATE))
+
+    def read(self):
+        return self.serial.readline().strip()
+
+    def write(self, data):
+        self.serial.write(data)
+
+    def read_laser_info(self):
+        data = {}
+        values = []
+        read = None
+        while read != "begin":
+            self.write("begin")
+            read = self.read()
+        while True:
+            read = self.read()
+            if read == "end":
+                break
+            print "Received %s" % read
+            try:
+                values.append(float(read) * 2)
+            except ValueError:
+                try:
+                    data.update(json.loads(read))
+                except:
+                    continue
+        data.update({
+            "values": values
+        })
+        return data
+
+if __name__ == "__main__":
+    argparser = argparse.ArgumentParser()
+    argparser.add_argument("serial_port", help="The serial port to read from")
+    args = argparser.parse_args()
+
+    print "Generating a scanner data visualization..."
+    scanner = Scanner.create(args.serial_port)
+    data = scanner.read_laser_info()
+
+    Visualizer.visualize(data)
+
+    print "Type a filename to save, otherwise press enter to exit..."
+    filename = raw_input()
+    if filename != "":
+        with open("data/%s.json" % filename, "w") as f:
+            f.write(json.dumps(data))
+\end{lstlisting}
 

### 2016-06-18 paper/paper.tex
update

@@
 The Arduino that we used to read in the voltage values from the photometer was also used to simultaneously control the stepper motors moving the sample.
-For one dimensional scans, we only moved one motor and scanned a single line across the target.
-For two dimensional scans, we oscillated the motor in one direction while shifting it slowly perpendicular to its direction of oscillation.
+For one dimensional scans, we scanned across the sample once and graphed the relative intensities as the laser passed over the sample.
+For two dimensional scans, we oscillated the sample in one direction while shifting it perpendicular to its direction of oscillation and mapped the relative intensies onto a 2D grid.
 
@@
   \centering
-  \includegraphics[width=10cm,height=6cm]{setup_diagram}
+  \includegraphics[width=12cm,height=8cm]{setup_diagram}
   \caption{Diagram of Components}
@@
 
+\newpage
+
 \begin{figure}[H]
   \centering
-  \includegraphics[width=6cm,height=7cm]{setup_picture}
+  \includegraphics[width=10cm,height=6cm]{setup_picture}
   \caption[caption]{3D printed components\footnotemark}
 \end{figure}
-\footnotetext{CADs available here\cite{github}:
-  \url{https://www.github.com/omgimanerd/im-firing-my-lazer}}
+\footnotetext{CADs available here:\cite{github}}
 
@@
 We set up various resolution test targets beneath our scanner and ran our scanner over each target. Based on the stepper motors\footnotemark
-\footnotetext{USPRO 28BYJ 5V 4-phase 5-wire stepper motors\cite{amazon}}
+\footnotetext{USPRO 28BYJ 5V 4-phase 5-wire stepper motors \cite{amazon}}
 and driver boards\footnotemark
-\footnotetext{ULN2003 driver board for Arduino\cite{amazon}}
+\footnotetext{ULN2003 driver board for Arduino \cite{amazon}}
 we were using, we approximated what the resolution of our setup would be.
@@
 
-$$ 3.067962\times10^{-3}in = 1.9557746\times10^{-2}mm $$
-$$ \frac{1\ line}{1.9557746\times10^{-2}mm} = 51.13\frac{lines}{mm} $$
-$$ 51.13\frac{lines}{mm} \div 2 \approx 25\frac{lines}{mm} $$
+$$ 3.067962\times10^{-3}in = 7.79262348\times10^{-2}mm $$
+$$ \frac{1\ line}{7.79262348\times10^{-2}mm} \approx 12.83\frac{lines}{mm} $$
 
 \par
-This number is only true, however, if our laser beam is an infinitesimally small point. Since this is not the case, our actual resolution is much lower.
+This number only holds true if our laser beam is an infinitesimally small point. Since this is not the case, our actual resolution is much lower.
+
+\section{Experimental Results for 1 Dimensional Scans}
 
@@
 
-\section{Experimental Results for 1 Dimensional Scans}
 \par
-Running the laser scanner over the actual resolution test targets above gave us a much clearer indicator of whether or not our scanner was actually able to resolve up to 25 $\frac{lines}{mm}$.
-We ran the laser directly over the four lines in each resolution test target while reading in the values, starting with the lowest resolution.
+Running the laser scanner over the actual resolution test targets above gave us a much clearer indicator of whether or not our scanner was actually able to resolve up to 12.83 $\frac{lines}{mm}$.
+We ran the laser directly over the five lines in each resolution test target while reading in the values, starting with the lowest resolution.
 
@@
 \par
-In figure 4, four discrete dips in the relative intensity read by the Arduino are visible as the laser passes over the 1.6 $\frac{lines}{mm}$ resolution test target.
+In figure 4, five discrete dips in the relative intensity read by the Arduino are visible as the laser passes over the 1.6 $\frac{lines}{mm}$ resolution test target.
 Each dip is distinguishable and corresponds to a line on the resolution test target.
@@
 Figures 5 to 11 show our scan data as we increase the resolution of our test target.
-As we increase the resolution of the test target, the variance in relative intensity between the lines and the space between them becomes muddled.
+As the resolution increases, the variance in relative intensity between the lines and the space between them becomes muddled.
 It is possible to see five discrete dips only up to 3.2 $\frac{lines}{mm}$.
@@
 \par
-For two dimensional scans, instead of running the sample in one direction under the laser, we oscillated it back and forth in the $y$ direction while slowing shifting it in the $x$ direction.
-This allowed us to produce a two-dimensional image of the lines on the resolution test target.
+For two dimensional scans, instead of running the sample in one direction under the laser, we oscillated it back and forth in the $x$ direction while shifting it in the $y$ direction.
+This allowed us to produce a two-dimensional image of the lines on the resolution test target by mapping the values onto a 2D grid.
 
@@
 We scaled the voltage received by the Arduino to a greyscale value and plotted it based on the motor's position to create the image.
-However, the motor would slightly drift after each oscillation, creating the slant in the line visible in the scan above.
+However, the motor would slightly drift after each oscillation, creating the slanted lines visible in the scan above.
 
@@
 We were able to reduce some of the slanting by manually accounting for the drift in the motors.
-Some noise is visible in both of the scans due to the flexing of test target since it was printed on standard printer paper.
+Some noise is visible in both of the scans due to the flexing of test target during scanning since it was printed on standard printer paper.
 

### 2016-06-18 lib/data.py
removed sachal's useless shit

@@ -1,29 +1,0 @@
-#!/usr/bin/python
-
-import json
-import sys
-import numpy as np
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-from scipy.fftpack import fft, ifft
-
-from pprint import pprint
-def readD(filename):
-    with open(filename) as data_file:
-        T = 1.00 / 800.0
-        N = 50    
-        data = json.load(data_file)
-        x = np.array(data)
-        yf = fft(x)
-        xf = np.linspace(0.0, 1.0/(2.0*T), N/2)
-        plt.plot(xf, 2.0/N * np.abs(yf[0:N/2]))
-        plt.grid()
-        plt.show()
-        #print(y)
-
-	#pprint(data)
-
-# What the fuck is this disgusting code
-# this is unreadable
-if __name__ == "__main__":
-    readD('hi.json'

### 2016-06-18 paper/paper.tex
another update
christine found a grammer error

@@
 This experiment was conducted in the Modern Physics class of 2016 at Stuyvesant High School.
-The goal was to build a laser scanner using a laser and a photodiode and find the maximum achievable resolution of the apparatus.
+The goal was to build a laser scanner using a laser and a photometer to find its maximum achievable resolution.
 \end{abstract}
@@
   \centering
-  \includegraphics[width=10cm,height=6cm]{setup_picture}
+  \includegraphics[width=8cm,height=10cm]{setup_picture}
   \caption[caption]{3D printed components\footnotemark}
